WIDS 2024 Final Project

### 2024-01-11 Code/R FIle.qmd
fixed theme

```{r}
#| message: FALSE
full_state_data |> 
  filter(year %% 4==0) |>
  ggplot(aes(x = percent_collective_bargain, y = party_state_average)) +
  geom_jitter(aes(color = regions), alpha = 0.15, width = 0.1, height = 0.1) +
  geom_smooth(method = "lm", aes(group = regions, color = regions), se = FALSE) +
  facet_wrap(~decade) +
  labs(
    title = "Percent Collective Bargaining vs Proportion of House Delegation That is Democratic",
    subtitle = "Regressed by Region",
    x = "Percent of Workers Covered by Collective Bargaining",
    y = "Proportion of House Delegation that is Democratic",
    color = "Region"
  )
```
These two graphs show very interesting results. First, we can see how unions have become politicized in the last 40 years. In the 1980s, there was almost no correlation between the amount of workers in a collective bargaining agreement and what the house delegation looked like in that state. By the 2010s, this had changed. From the second graph, we can see that the North Central and South regions are the main drivers behind this, seen in the steepening of the regression slope.

>>>>

```{r}
#| message: FALSE
full_state_data |> 
  filter(year %% 4==0) |>
  ggplot(aes(x = percent_collective_bargain, y = party_state_average)) +
  geom_jitter(aes(color = regions), alpha = 0.15, width = 0.1, height = 0.1) +
  geom_smooth(method = "lm", aes(group = regions, color = regions), se = FALSE) +
  facet_wrap(~decade) +
  theme_light() +
  labs(
    title = "Percent Collective Bargaining vs Proportion of House Delegation That is Democratic",
    subtitle = "Regressed by Region",
    x = "Percent of Workers Covered by Collective Bargaining",
    y = "Proportion of House Delegation that is Democratic",
    color = "Region"
  )
```
These two graphs show very interesting results. First, we can see how unions have become politicized in the last 40 years. In the 1980s, there was almost no correlation between the amount of workers in a collective bargaining agreement and what the house delegation looked like in that state. By the 2010s, this had changed. From the second graph, we can see that the North Central and South regions are the main drivers behind this, seen in the steepening of the regression slope.
